\LARGE \bf Portfolio Optimization Based on a Complex Networks Model\\ \normalsize TODO: propose a better title

### 2017-05-05 tex/article.tex
diplić

\title{\LARGE \bf Portfolio Optimization Based on a Complex Networks Model\\TODO: propose a better title}

@@

  Following are the descriptions of two key components in the algorithm: creating the graph, and choosing assets for the portfolio...

@@

  Afterwards, for each observed pair $(i,j)$ that breaks the threshold we add into graph vertices $i$ and $j$, and a weighed link going from $i$ to $j$, with weight $w_{i,j}^{(t)}$ obtained as:

@@

>>>>

\title{\LARGE \bf Portfolio Optimization Based on a Complex Networks Model\\
  \normalsize TODO: propose a better title}

@@

  Following are the descriptions of two key components in the algorithm: graph of preference relations, and choosing assets for the portfolio...

  \subsection{Graph of preference relations}

  This is a graph whose vertices represent assets and edges represent how much more is one asset preferred over the other.
  An example is shown on the Fig. \ref{fig:graph}.
  The measure of this preference is determined by a statistical arbitrage algorithm, and it corresponds to the magnitude of two assets' price ratio going out of what is statistically considered `normal' range.
  This is illustrated on Fig. \ref{fig:devmag}.

  \begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{graphics/output_0573.pdf}
    \caption{TODO: put image with weights on edges}
    \label{fig:graph}
  \end{figure}

  \begin{figure}[htb]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphics/deviation-magnitude.png}
    \caption{TODO: put a better image, this is just for a placeholder}
    \label{fig:devmag}
  \end{figure}

  \subsection{Preference flow}

@@

  Afterwards, for each observed pair $(i,j)$ that breaks the threshold we add into graph vertices $i$ and $j$, and a weighed edge going from $i$ to $j$, with weight $w_{i,j}^{(t)}$ obtained as:

@@

  From previously obtained graph it is possible to tell which pair has the highest preference.
  However it is still not possible to tell which asset is the most preferable one, or obtain the measure of preference for individual assets, directly.
  For this we need to calculate some sort of preference flow, as if it were water going through pipes of widths corresponding to edge weights, from one asset to another.
  A quick way to do this is by using the potential method as described in \cite{caklovic}.
